---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# simTransmission

<!-- badges: start -->
<!-- badges: end -->

The goal of simTransmission is to provides functions to simulate, summarize and plot transmission network and its corresponding phylogenetic tree.

## Installation

You can install simTransmission in R using the following command:

``` r
devtools::install_github('Huimin-stat/simTransmission')
```

## Example

This is a basic example which shows you how to simulate a transmission and plot the transmission network:

```{r example, message=FALSE, dpi=200}
library(simTransmission)
set.seed(23)
transmission <- simTransmission(inf_rate = c(0.423,0.3), inf_rate_time = c(0,50), diag_rate = 0.143, rec_rate_asy = 0.052, rec_rate_sym = 0.0476, death_prop = 0.05, death_rate = 0.0357, inf_rate_diag = 0.02, asy_prop = 0.179, ngeneration = 8)
transmission1 <- simTransmission(inf_rate = c(0.423,0.3), inf_rate_time = c(0,50), diag_rate = 0.143, rec_rate_asy = 0.052, rec_rate_sym = 0.0476, death_prop = 0.05, death_rate = 0.0357, inf_rate_diag = 0.02, asy_prop = 0, ngeneration = 8)
times <- c(15, 30, 45, 60, 75)
cases.plot(transmatrix = transmission, times)
cases.plot(transmatrix = transmission1, times)

trunc <- timeTruncate(transmission1, 7)

set.seed(23)
(modeltree <- modelTreefromTransmission(trunc$truncTM))
(coaltree <- simCoalModeltree(1, modeltree, 0.8))
plotTree(modeltree)
plotTree(coaltree)

trunc1 <- timeTruncate(transmission, 15)
plotTransNet(trunc1$truncTM, trunc1$index_sym_latent, trunc1$index_sym_diagnosed, trunc1$index_sym_recovered, trunc1$index_asy_infectious, trunc1$index_asy_recovered, trunc1$index_dead)

trunc2 <- timeTruncate(transmission1, 15)
plotTransNet(trunc2$truncTM, trunc2$index_sym_latent, trunc2$index_sym_diagnosed, trunc2$index_sym_recovered, trunc2$index_asy_infectious, trunc2$index_asy_recovered, trunc1$index_dead)

```



