---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# simTransmission

<!-- badges: start -->
<!-- badges: end -->

The goal of simTransmission is to provides functions to simulate, summarize and plot transmission network and its corresponding phylogenetic tree.

## Installation

You can install simTransmission in R using the following command:

``` r
devtools::install_github('Huimin-stat/simTransmission')
```

## Example

This is a basic example which shows you how to simulate a transmission and plot the transmission network:

```{r example}
library(simTransmission)
trans <- simTransmission(inf_rate = c(0.423,0.3), inf_rate_time = c(0,50), diag_rate = 0.143, rec_rate_asy = 0.052, rec_rate_sym = 0.0476, death_prop = 0.05, death_rate = 0.0357, inf_rate_diag = 0.02, asy_prop = 0.179, ngeneration = 7)
trunc <- timeTruncate(trans, 12)
plotTransNet(trunc$truncTM, trunc$index_sym_latent, trunc$index_sym_diagnosed, trunc$index_sym_recovered, trunc$index_asy_infectious, trunc$index_asy_recovered, trunc$index_dead)

```


In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!
